ACNP 2024 MS ANXIETY

### 2024-07-25 scripts/ACNP2024_MSAnxiety.Rmd
Add files via upload

---
title: "MS Prelim Data K23"
author: "Erica Baller"
date: "2/25/2022"
output:
  html_document: default
  pdf_document: default
---

@@

Inclusion criteria for Anxious Group
  1) Have an ICD10 F3* code (in our sample, people have F41.1; 41.3; 41.8; 41.9)
        (may use this later)- https://www.nami.org/About-Mental-Illness/Treatments/Mental-Health-Medications

Inclusion criteria for Healthy Group
  1) No F* diagnoses
  2) At least 1 PHQ2 or PHQ9 with a documented 0
  3) Free of psychiatric medications per NAMI website

Exclusions
  If you received the MS protocol or had a diagnosis of MS but never actually saw an MS provider, we cannot be sure that the diagnosis of MS is truly valid, as it is hard to diagnose anyway.
  If you did not have a diagnosis of depression and never completed a PHQ2 or 9, and had no history of medications, we could not safely confirm nor deny the presence of depression. These subjects were excluded from future analyses. We could consider adding these to the healthy group maybe, but not too inclined to do that right now.

@@

## Anxiety within/outside network interaction
```{r anxiety_net_intx}

## demographics

### BEST SPLIT IS STRATIFYING ON ANXIETY MEDS!!!! Better than on variable that includes anxietyGroupVar(meds + anxiety diagnoses), or anxiety diagnosis alone
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietyGroupVar != 0,])
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$Has.Anxietydx.AND.AntianxietymedGroupVar != 0,])

#clean up data frame
df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
  filter(anxietyGroupVar != 0) %>% #lose 93, n now 719
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(anxietyGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
  mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
  mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
  mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
  mutate(Benzo_status = as.factor(Benzo_status)) %>%
  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, Anxiolytics_status, Has.anxietydx, Benzo_status, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -Anxiolytics_status, -Has.anxietydx, -Benzo_status) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

#simple t test, disease within versus outside anxiety network; mean within anxiety net: 0.5426694 affected, mean outside anxiety network = 0.3062429, T=57.44, p<2.2*10^-16, 95% CI 0.22-0.24
#MS+Anxiety, MS-Anxiety, meds + anxiety dx, true normal = 0.3850697; MS+ anxiety: ; MS-anxiety: 0.3672053
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"])
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])

#Anxiety dx vs no anxiety dx
#anxiety dx: 0.3785979; no anxiety dx: 0.3723245
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.anxietydx==1])
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.anxietydx==0])

#On.Anxiolytics vs Off.Anxiolytics
#on anxiolytics: 0.415625; off anxiolytics:0.3664898
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Anxiolytics_status=="On.Anxiolytics"])
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Anxiolytics_status=="Off.Anxiolytics"])

#On.Benzos vs Off.Benzos
#on benzos: 0.4022933; off benzos:0.372135
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Benzo_status=="On.Benzos"])
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Benzo_status=="Off.Benzos"])

#Has.Anxietydx.Or.Antianxietymed
#on benzos: 0.4022933; off benzos:0.372135
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.Anxietydx.Or.Antianxietymed=="On.Benzos"])
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.Anxietydx.Or.Antianxietymed=="Off.Benzos"])

#histos
hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")

## Means of separate groups:

#t test, t = 63.621, df = 718, p-value < 2.2e-16; 95 percent confidence interval:0.2349467 0.2499088, mean diff: 0.2424277 
within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
summary(within_vs_outside_anxiety_net_t)

 #simple lmer, confirms T; -63.62   <2e-16 ***
disease_within_vs_outside_anxiety_net_lmer <- lmer(proportion_affected ~ Network + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_lmer)

 #Net by sex, confirms T; -63.62   <2e-16, but no sex differences (p=0.179)
disease_within_vs_outside_anxiety_net_sex_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_sex_lmer)

 #simple lmer, confirms network: -63.621  < 2e-16 , Pat age: 6.338 4.12e-10
disease_within_vs_outside_anxiety_net_age_lmer <- lmer(proportion_affected ~ Network + PAT_AGE_AT_EXAM + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_age_lmer)

#Age * network interaction, don't know if this is valid at all. outside > w/in net: -12.718  < 2e-16 ***; pat age = 6.837  1.6e-11 ***, NetworkNonanxiety_network:PAT_AGE_AT_EXAM -2.852  0.00447 
disease_within_vs_outside_anxiety_net_age_intx_lmer <- lmer(proportion_affected ~ Network*PAT_AGE_AT_EXAM + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_age_intx_lmer)

#diagnosis: NS
diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer)

#Diagnosis: NS
confint(diagnosis_by_network_interaction_lmer)

## Anxiety network x anxiolytics status
#Network (nonanxiety <anxiety network) : T = -58.141   <2e-16 ***; Anxiolytic status: On.anxiolytics>off.anxiolytics; T= 2.473   0.0136 *  
#Mean prop affected: on anxiolytics: 0.415625;  off anxioloytics: 0.3664898

disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer <- lmer(proportion_affected ~ Network*Anxiolytics_status + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
confint(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)

## Anxiety network x benzo status
#Network (nonanxiety <anxiety network) : T = -54.535   <2e-16***; Anxiety status: T = 0.462    P = 0.645

disease_within_vs_outside_anxiety_net_by_benzo_lmer <- lmer(proportion_affected ~ Network*Benzo_status + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
confint(disease_within_vs_outside_anxiety_net_by_benzo_lmer)

## Anxiety network x anxiety diagnosis
#Network (nonanxiety <anxiety network) : T = -54.535   <2e-16***; Anxiety status: T = 0.462    P = 0.645

disease_within_vs_outside_anxiety_net_by_anxietydx_lmer <- lmer(proportion_affected ~ Network*Has.anxietydx + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
confint(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
```

#Anxiety network interactions and uncinate alone
```{r anxiety_net_intx}

## demographics

make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$Has.Anxietydx.AND.AntianxietymedGroupVar != 0,])

#clean up data frame
cleaned_df <- df_demo_and_fascicles %>%
  filter(Has.Anxietydx.AND.AntianxietymedGroupVar != 0) %>% #lose 93, n now 719
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(Has.Anxietydx.AND.AntianxietymedGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
  mutate(mean_uncinate_injury = (UF_L_prop + UF_R_prop)/2) %>%
  mutate(mean_uncinate_and_fornix_injury = (UF_L_prop + UF_R_prop + F_R_prop + F_L_prop)/2) %>%
  ungroup()

df_empi_dx_network_proportions <- cleaned_df %>%
  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

#histos
hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")
hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS+Anxiety"], main = "Uncinate Injury in Anxious Patients", xlab = "Proportion Affected")
hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS-Anxiety"], main = "Uncinate Injury in Healthyish Patients", xlab = "Proportion Affected")

## Means of separate groups:

#t test, 
within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
within_vs_outside_anxiety_net_t

#diagnosis: 
diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer)
confint(diagnosis_by_network_interaction_lmer)

#Net by sex, confirms T; -63.62   <2e-16, but no sex differences (p=0.179)
disease_within_vs_outside_anxiety_net_sex_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_sex_lmer)

#t test uncinate alone
mean_uncinate_by_dx_t <- t.test(cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
mean_uncinate_by_dx_t

#diagnosisxmean_uncinate: 
diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_injury ~ Diagnosis, data = cleaned_df)
summary(diagnosis_by_network_interaction_lmer)
confint(diagnosis_by_network_interaction_lmer)

#diagnosisxmean_uncinate+fornix: 
diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_and_fornix_injury ~ Diagnosis, data = cleaned_df)
summary(diagnosis_by_network_interaction_lmer)
confint(diagnosis_by_network_interaction_lmer)

#### if I decide later I want to look at L and right uncinate alone

#t test uncinate alone, Left,
l_uncinate_by_dx_t <- t.test(cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
l_uncinate_by_dx_t

#t test uncinate alone, right, remember everybody is double counted!!!! so this needs to be fixed.
r_uncinate_by_dx_t <- t.test(cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
r_uncinate_by_dx_t

## Anxiety burden severity ranking

I am wondering here if, as my brain wants to think, that things in the chart reflect severity of anxiety. For example, I'd expect people with dep and anxiety comorbidity and on meds would be the sickest, followed by anxiety + on meds, then on meds, then anxiety dx, then healthyish. I am going to do a t-test comparing proportion of disease over whole brain, over anxiety net, and over uncinate in each of those groups as compared to the healthy group, and rank the T to see if that pattern bears out. And if it does, do some sort of regression.
```{r anxiety_burden_severity_ranking }
#variables_to_evaluate <- c("Has.Anxietydx.AND.AntianxietymedGroupVar")
df_disease_burden_unc_and_anx_net <- df_demo_and_fascicles %>%
  filter(oAnxiety.And.Dep.And.AnxietyMedsGroupVar != "unclassified") %>%
  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxiety.And.Dep.And.AnxietyMedsGroupVar, osex)

tibble_n <- df_disease_burden_unc_and_anx_net %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>% 
  summarise(n())

tibble_overall_disease <- 
  df_disease_burden_unc_and_anx_net %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
  summarize(mean_size = mean(proportion_volume_lost_per_total_network_size_sum))

tibble_overall_summaries <- 
  df_disease_burden_unc_and_anx_net %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
tibble_overall_summaries

tibble_overall_summaries_by_sex <- 
  df_disease_burden_unc_and_anx_net %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar, osex) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_by_sex

  tibble_overall_summaries_females <- 
  df_disease_burden_unc_and_anx_net %>% 
  filter(osex == "Female") %>%
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_females

    tibble_overall_summaries_males <- 
  df_disease_burden_unc_and_anx_net %>% 
  filter(osex == "Male") %>%
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_males

  ### analyses

#### plots
```{r}
  #proportion injured over whole brain
prop_injured_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_per_total_network_size_sum, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_by_anxiety_burden_plot

  #proportion injured over anxiety net
prop_injured_anxiety_net_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_anxiety_net_by_anxiety_burden_plot

  #proportion injured over nonanxiety net
prop_injured_nonanxiety_net_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_nonanxiety_net_by_anxiety_burden_plot

  #proportion injured over R Uncinate prop
prop_injured_R_uncinate_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=UF_R_prop, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_R_uncinate_by_anxiety_burden_plot

  #proportion injured over L Uncinate prop
prop_injured_L_uncinate_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=UF_L_prop, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_L_uncinate_by_anxiety_burden_plot

prop_injured_by_anxiety_burden_and_sex_plot <- ggboxplot(df_disease_burden_unc_and_anx_net, x = "oAnxiety.And.Dep.And.AnxietyMedsGroupVar", y = "proportion_volume_lost_per_total_network_size_sum", color = "osex",
          palette = c("#00AFBB", "#E7B800")) +
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_by_anxiety_burden_and_sex_plot

#Anxiety network interactions and uncinate alone, TRUE HEALTHY
```{r anxiety_net_intx}

## demographics

make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified",])

#clean up data frame
cleaned_df <- df_demo_and_fascicles %>%
  filter(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified") %>% #lose 93, n now 719
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
  mutate(mean_uncinate_injury = (UF_L_prop + UF_R_prop)/2) %>%
  mutate(mean_uncinate_and_fornix_injury = (UF_L_prop + UF_R_prop + F_R_prop + F_L_prop)/2) %>%
  ungroup()

df_empi_dx_network_proportions <- cleaned_df %>%
  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

#histos
hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")
hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS+Anxiety"], main = "Uncinate Injury in Anxious Patients", xlab = "Proportion Affected")
hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS-Anxiety"], main = "Uncinate Injury in Healthyish Patients", xlab = "Proportion Affected")

## Means of separate groups:

#t test, 
within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
within_vs_outside_anxiety_net_t

#diagnosis: 
diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer)
confint(diagnosis_by_network_interaction_lmer)

#Net by sex, confirms T; -63.62   <2e-16, but no sex differences (p=0.179)
disease_within_vs_outside_anxiety_net_sex_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_sex_lmer)

#t test uncinate alone
mean_uncinate_by_dx_t <- t.test(cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
mean_uncinate_by_dx_t

#diagnosisxmean_uncinate: 
diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_injury ~ Diagnosis, data = cleaned_df)
summary(diagnosis_by_network_interaction_lmer)
confint(diagnosis_by_network_interaction_lmer)

#diagnosisxmean_uncinate+fornix: 
diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_and_fornix_injury ~ Diagnosis, data = cleaned_df)
summary(diagnosis_by_network_interaction_lmer)
confint(diagnosis_by_network_interaction_lmer)

#### if I decide later I want to look at L and right uncinate alone

#t test uncinate alone, Left,
l_uncinate_by_dx_t <- t.test(cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
l_uncinate_by_dx_t

#t test uncinate alone, right, remember everybody is double counted!!!! so this needs to be fixed.
r_uncinate_by_dx_t <- t.test(cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
r_uncinate_by_dx_t

## Anxiety burden severity ranking true healthy

I am wondering here if, as my brain wants to think, that things in the chart reflect severity of anxiety. For example, I'd expect people with dep and anxiety comorbidity and on meds would be the sickest, followed by anxiety + on meds, then on meds, then anxiety dx, then healthyish. I am going to do a t-test comparing proportion of disease over whole brain, over anxiety net, and over uncinate in each of those groups as compared to the healthy group, and rank the T to see if that pattern bears out. And if it does, do some sort of regression.
```{r anxiety_burden_severity_ranking }
#variables_to_evaluate <- c("Has.Anxietydx.AND.AntianxietymedGroupVar")
df_disease_burden_unc_and_anx_net_true_healthy <- df_demo_and_fascicles %>%
  filter(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified") %>%
  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, osex)

tibble_n <- df_disease_burden_unc_and_anx_net_true_healthy %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>% 
  summarise(n())

tibble_overall_disease <- 
  df_disease_burden_unc_and_anx_net_true_healthy %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
  summarize(mean_size = mean(proportion_volume_lost_per_total_network_size_sum))

tibble_overall_summaries <- 
  df_disease_burden_unc_and_anx_net_true_healthy %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
tibble_overall_summaries

tibble_overall_summaries_by_sex <- 
  df_disease_burden_unc_and_anx_net_true_healthy %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, osex) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_by_sex

>>>>

---
title: "ACNP 2024 MS ANXIETY"
author: "Erica Baller"
date: "7/1/2024"
output:
  html_document: default
  pdf_document: default
---

@@

Inclusion criteria for Anxious Group
  1) Have an ICD10 F4* code (in our sample, people have F41.1; 41.3; 41.8; 41.9)
        (may use this later)- https://www.nami.org/About-Mental-Illness/Treatments/Mental-Health-Medications

Inclusion criteria for Healthy Group
  1) No F* diagnoses
  2) At least 1 PHQ2 or PHQ9 with a documented 0
  3) Free of psychiatric medications per NAMI website (plus editions per Dr. Baller)

Exclusions
  If you received the MS protocol or had a diagnosis of MS but never actually saw an MS provider, we cannot be sure that the diagnosis of MS is truly valid, as it is hard to diagnose anyway.
  If you did not have a diagnosis of depression and never completed a PHQ2 or 9, and had no history of medications, we could not safely confirm nor deny the presence of anxiety. These subjects were excluded from future analyses. We could consider adding these to the healthy group maybe, but not too inclined to do that right now.

@@

#COLLAPSE anxiety dx and antianxiety meds with those plus depression, and anxiety dx OR on anxiety meds into 1 group -->> THIS IS THE MONEY

### Double check that people in each group are correct
```{r gut_check}

#want to make sure that people in healthy are NOT on anxiolytics or have dx, that people in the second group have one OR the other, and that people in the third group have BOTH

#make data frame
df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
   filter (anxiety_dose != 3)

###true healthy
num_people_in_healthy_with_0_for_Has.Anxiety_and_On.Anxiolytics <- length(which(df_demo_and_fascicles_no_unclass_anxiety_dose$On.Anxiolytics ==0 & df_demo_and_fascicles_no_unclass_anxiety_dose$Has.anxietydx ==0))
print(paste0("num_people_in_healthy_with_0_for_Has.Anxiety_and_On.Anxiolytics-> ", num_people_in_healthy_with_0_for_Has.Anxiety_and_On.Anxiolytics, " and num in this group from groupVar -> ", sum(df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0)))

### Anxiety dose = 1
num_people_in_Anxiety_OR_On.Anxiolytics <- length(which((df_demo_and_fascicles_no_unclass_anxiety_dose$On.Anxiolytics ==1 | df_demo_and_fascicles_no_unclass_anxiety_dose$Has.anxietydx ==1) &
(df_demo_and_fascicles_no_unclass_anxiety_dose$On.Anxiolytics != df_demo_and_fascicles_no_unclass_anxiety_dose$Has.anxietydx)))

print(paste0("num_people_in_Anxiety_OR_On.Anxiolytics-> ", num_people_in_Anxiety_OR_On.Anxiolytics, " and num in this group from groupVar -> ", sum(df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1)))

#severe anxiety
num_people_in_Anxiety_AND_Anxiolytics <- length(which(df_demo_and_fascicles_no_unclass_anxiety_dose$On.Anxiolytics ==1 & df_demo_and_fascicles_no_unclass_anxiety_dose$Has.anxietydx ==1))
print(paste0("num_people_in_Anxiety_AND_Anxiolytics-> ", num_people_in_Anxiety_AND_Anxiolytics, " and num in this group from groupVar -> ", sum(df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2)))

print(paste0("total n -> ",num_people_in_healthy_with_0_for_Has.Anxiety_and_On.Anxiolytics + num_people_in_Anxiety_OR_On.Anxiolytics + num_people_in_Anxiety_AND_Anxiolytics, " and row # in data frame -> ", dim(df_demo_and_fascicles_no_unclass_anxiety_dose)[1]))

```
### Overlap with depression group
```{r overlap_with_dep_group}
#### 53.4% overlap total
